Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
updated the resources section

\documentclass{template}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}

@@

\section{Resources}

Our online artifacts of our completed pilot study, such as 
the summary, results, and resulting browser changes are below:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}
\item \url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}
\end{itemize}

Subtitled screen videos:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://people.torproject.org/~dcf/uxsprint2015/}
\end{itemize}

>>>>

\documentclass{template}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}
\usepackage{hyperref}

@@

\section{Resources}
\noindent Our online artifacts of the work done during this class, Fall 2015,
are below: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \href{https://github.com/lindanlee/circumvention-ux-tor}{github repo with experiment plans, code, and paper}
\item \href {https://github.com/lindanlee/circumvention-ux-tor/blob/master/pilot/1-strict.mp4}{pilot video 1}
	\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/pilot/2-lax.mp4}{pilot video 2}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/setup-environment}{experimental setup code: firewall and screen capture} 
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/takedown-environment}{experimental takedown code: saving files and cleanup} 
\end{itemize}

%%  FROM ANONYMITY UX STUDY 
Our online artifacts of study of Tor as an anonymity tool, such as 
the summary, results, and resulting browser changes are below:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \href{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}{blog post summary}
\item \href{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}{changes made to Tor}
\item \href{https://people.torproject.org/~dcf/uxsprint2015/}{subtitled screen videos}
\end{itemize}
